Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-08-07 manuscript.tex
Update manuscript and correct errors

\begin{figure}[htbp]
    \centering
    \input{tikz/frustrum.tikz}
    \caption{View frustum for spacecraft sensor modeling\label{fig:view_frustrum}}
\end{figure}
We assume that the spacecraft is located at \(\rpos\) in the asteroid fixed frame.
We define a camera fixed frame, \( \vc{c}_i \in \R^3 \), which is defined with respect to the spacecraft body fixed frame, \( \vc{b}_i \).
The camera/sensor is aligned with \gls{view_axis} in the spacecraft fixed frame and we define an additional vector, termed the up axis \gls{up_axis} as the vertical direction of the image plane. 
Finally, the standard basis is completed with \(  \gls{right_axis} = \gls{view_axis} \times \gls{up_axis} \) which defines a reference frame attached to the image plane of the sensor.
Furthermore, we model the laser ranging sensor as having a fixed field of view defined by the angles \( \gls{fov_h}, \gls{fov_v}\), defining the vertical and horizontal fields of view.
In order to simulate depth measurements we need to determine the transformation of locations in the image frame to the small body fixed frame. 
Given the view axis, and a chosen distance \gls{view_distance}, we can define a viewing \gls{frustum} associated with the sensor. 
We can compute the vectors associated with the maximum extents of the far plane as follows.
The half height and width of the far plane, at a distance \( d \), are computed as
\begin{align*}
    H = d \tan \frac{\alpha}{2} , \\
    W = d \tan \frac{\beta}{2} .
\end{align*}
From these values, the extents of the far plane are defined by the vectors
\begin{align*}
    A = \vc{c}_1 + H \vc{c}_3 - W \vc{c}_2 , \\
    B = \vc{c}_1 + H \vc{c}_3 + W \vc{c}_2, \\
    C = \vc{c}_1 - H \vc{c}_3 + W \vc{c}_2, \\
    D = \vc{c}_1 - H \vc{c}_3 - W \vc{c}_2.
\end{align*}
The view frustum is visualized in~\cref{fig:view_frustrum} and allows for any vector in the field of view to be defined as a linear combination of the extents of the far plane.
% tylee: not sure what "befined" means? 
% shankar: should have been "defined"

>>>>

\begin{figure}[htbp]
    \centering
    \input{tikz/frustrum.tikz}
    \caption{View frustum for spacecraft sensor modeling\label{fig:view_frustrum}}
\end{figure}
We assume that the spacecraft is located at \(\rpos\) in the asteroid fixed frame.
We define a camera fixed frame, \( \vc{c}_i \in \R^3 \), which is defined with respect to the spacecraft body fixed frame, \( \vc{b}_i \).
The camera/sensor is aligned with \( \vc{c}_1 \) in the spacecraft fixed frame and we define an additional vector, termed the up axis \( \vc{c}_3 \) as the vertical direction of the image plane. 
Finally, the standard basis is completed with \(  \vc{c}_2 = \vc{c}_1 \times \vc{c}_3 \) which defines a reference frame attached to the image plane of the sensor.
Furthermore, we model the laser ranging sensor as having a fixed field of view defined by the angles \( \alpha, \beta \), defining the vertical and horizontal fields of view.
In order to simulate depth measurements we need to determine the transformation of locations in the image frame to the small body fixed frame. 
Given the view axis, and a chosen distance \( d  \in \R^1 \), we can define a viewing frustum associated with the sensor. 
We can compute the vectors associated with the maximum extents of the far plane as follows.
The half height and width of the far plane, at a distance \( d \), are computed as
\begin{align*}
    H = d \tan \frac{\alpha}{2} , \\
    W = d \tan \frac{\beta}{2} .
\end{align*}
From these values, the extents of the far plane are defined by the vectors
\begin{align*}
    A = \vc{c}_1 + H \vc{c}_3 - W \vc{c}_2 , \\
    B = \vc{c}_1 + H \vc{c}_3 + W \vc{c}_2, \\
    C = \vc{c}_1 - H \vc{c}_3 + W \vc{c}_2, \\
    D = \vc{c}_1 - H \vc{c}_3 - W \vc{c}_2.
\end{align*}
The view frustum is visualized in~\cref{fig:view_frustrum} and allows for any vector in the field of view to be defined as a linear combination of the extents of the far plane.
% tylee: not sure what "befined" means? 
% shankar: should have been "defined"
